Survey of Misuses of the KS-Test

### 2021-12-02 Manuscript/manuscript.tex
Added to the reference folder and fixed a bibliography issue where it would not appear in the manuscript
Added tests for assumptions of KS-Test. Added Weiss reference. Added rough abstract.

\begin{abstract}
Abstract here.
\end{abstract}

@@

@@

>>>>

\begin{abstract}
The Kolmogorov–Smirnov (KS) test is one the most popular goodness-of-fit tests for comparing a sample with a hypothesized parametric distribution. Nevertheless, it has often been misused. The standard one-sample KS test applies to independent, continuous data with a hypothesized distribution that is completely specified. It is not uncommon, however, to see in the literature that it was applied to dependent, discrete, or rounded data, with hypothesized distributions containing estimated parameters. For example, it has been “discovered” multiple times that the test is too conservative when the parameters are estimated [e.g., 39]. This paper aims to survey the misuses of the KS test, demonstrate their consequences through simulation, and provide remedies as needed.
\end{abstract}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
 & Tests\_Samples & Power\_Level \\ 
  \hline
1 & 10000, 10 & 0.95 \\ 
  2 & 10000, 100 & 0.96 \\ 
  3 & 10000, 1000 & 0.95 \\ 
  4 & 10, 10000 & 0.90 \\ 
  5 & 100, 10000 & 0.92 \\ 
  6 & 1000, 10000 & 0.94 \\ 
   \hline
\end{tabular}
\end{table}

@@

Here is an example citation: \citet{Steinskog}
